---
title: "survey_biological for Aimee and Lindsey"
author: "Fonseca"
date: "4/26/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r cars}
library(readxl)
survey_data <- read_excel("survey_data.xlsx", sheet = "Data 4.21.2020")
survey_data1 <- data.frame(survey_data)
```

Contingency table Years*FUA-MSC:

```{r , echo=T}
library(dplyr)
library(knitr)
#Create cross table
t1 <- table(survey_data$Years,survey_data$"FUA-MSC")
#Selecting order for rows and cols
#y <- c("Greater than once/month", "Greater than 5 times/month", "1-5 times/year", "5-10 times/year", "Never")
x <- c("Less than 5 years", "5-10 years", "10-20 years", "Greater than 20 years")
#t1 <- addmargins(t1)
t1 <- as.data.frame.matrix(t1)
t2 <- t1 %>%  mutate(sumcol2_3= t1[,2]+t1[,3])
rownames(t2)[1] <- "10-20 years"
rownames(t2)[2] <- "5-10 years	"
rownames(t2)[3] <- "Greater than 20 years	"
rownames(t2)[4] <- "Less than 5 years"
t2 <- t2[x,]


kable(t2, caption = "Contingency table Years*FUA-MSC") 
```

Contingency table FUBM-MSC:

```{r , echo=T}
library(dplyr)
library(knitr)
#Create cross table
t3 <- table(survey_data$Years,survey_data$"FUBM-MSC")
#Selecting order for rows and cols
#y <- c("Greater than once/month", "Greater than 5 times/month", "1-5 times/year", "5-10 times/year", "Never")
x <- c("Less than 5 years", "5-10 years", "10-20 years", "Greater than 20 years")
#t1 <- addmargins(t1)
t3 <- as.data.frame.matrix(t3)
t4 <- t3 %>%  mutate(sumcol2_3= t3[,2]+t3[,3])
rownames(t4)[1] <- "10-20 years"
rownames(t4)[2] <- "5-10 years	"
rownames(t4)[3] <- "Greater than 20 years	"
rownames(t4)[4] <- "Less than 5 years"
t4 <- t4[x,]


kable(t4, caption = "Contingency table Years*FUBM-MSC") 
```

Contingency table	Years*FU-PRP
```{r , echo=T}
library(dplyr)
library(knitr)
#Create cross table
t5 <- table(survey_data$Years,survey_data$"FU-PRP")
#Selecting order for rows and cols
#y <- c("Greater than once/month", "Greater than 5 times/month", "1-5 times/year", "5-10 times/year", "Never")
x <- c("Less than 5 years", "5-10 years", "10-20 years", "Greater than 20 years")
#t1 <- addmargins(t1)
t5 <- as.data.frame.matrix(t5)
t6 <- t5 %>%  mutate(sumcol2_3= t5[,2]+t5[,3])
rownames(t6)[1] <- "10-20 years"
rownames(t6)[2] <- "5-10 years	"
rownames(t6)[3] <- "Greater than 20 years	"
rownames(t6)[4] <- "Less than 5 years"
t6 <- t6[x,]


kable(t6, caption = "Contingency table Years*FU-PRP") 
```

Contingency table	Years*FU-IRAP
```{r , echo=T}
library(dplyr)
library(knitr)
#Create cross table
t7 <- table(survey_data$Years,survey_data$"FU-IRAP")
#Selecting order for rows and cols
#y <- c("Greater than once/month", "Greater than 5 times/month", "1-5 times/year", "5-10 times/year", "Never")
x <- c("Less than 5 years", "5-10 years", "10-20 years", "Greater than 20 years")
#t1 <- addmargins(t1)
t7 <- as.data.frame.matrix(t7)
t8 <- t7 %>%  mutate(sumcol2_3= t7[,2]+t7[,3])
rownames(t8)[1] <- "10-20 years"
rownames(t8)[2] <- "5-10 years	"
rownames(t8)[3] <- "Greater than 20 years	"
rownames(t8)[4] <- "Less than 5 years"
t8 <- t8[x,]


kable(t8, caption = "Contingency table Years*FU-IRAP") 
```

Contingency table	Years*FU-PS
```{r , echo=T}
library(dplyr)
library(knitr)
#Create cross table
t9 <- table(survey_data$Years,survey_data$"FU-PS")
#Selecting order for rows and cols
#y <- c("Greater than once/month", "Greater than 5 times/month", "1-5 times/year", "5-10 times/year", "Never")
x <- c("Less than 5 years", "5-10 years", "10-20 years", "Greater than 20 years")
#t1 <- addmargins(t1)
t9 <- as.data.frame.matrix(t9)
t10 <- t9 %>%  mutate(sumcol2_3= t9[,2]+t9[,3])
rownames(t10)[1] <- "10-20 years"
rownames(t10)[2] <- "5-10 years	"
rownames(t10)[3] <- "Greater than 20 years	"
rownames(t10)[4] <- "Less than 5 years"
t10 <- t10[x,]


kable(t10, caption = "Contingency table Years*FU-PS") 
```

Contingency table	Specialty*FUA-MSC
```{r , echo=T}
library(dplyr)
library(knitr)
#Create cross table
t11 <- table(survey_data$Specialty,survey_data$"FUA-MSC")

#Selecting order for rows and cols
#y <- c("Greater than once/month", "Greater than 5 times/month", "1-5 times/year", "5-10 times/year", "Never")
#x <- c("Less than 5 years", "5-10 years", "10-20 years", "Greater than 20 years")
#t1 <- addmargins(t1)
t11 <- as.data.frame.matrix(t11)
t12 <- t11 %>%  mutate(sumcol2_3= t11[,2]+t11[,3])
rownames(t12)[1] <- "ACVS diplomate (large animal/equine)"
rownames(t12)[2] <- "ACVSMR diplomate (equine)	"
rownames(t12)[3] <- "Both ACVS and ACVSMR diplomate	"
#rownames(t12)[4] <- "Both ACVS and ACVSMR diplomate"
#t12 <- t12[x,]


kable(t12, caption = "Contingency table Specialty*FUA-MSC") 
```

Contingency table	Specialty*FUBM-MSC
```{r , echo=T}
library(dplyr)
library(knitr)
#Create cross table
t13 <- table(survey_data$Specialty,survey_data$"FUBM-MSC")

#Selecting order for rows and cols
#y <- c("Greater than once/month", "Greater than 5 times/month", "1-5 times/year", "5-10 times/year", "Never")
#x <- c("Less than 5 years", "5-10 years", "10-20 years", "Greater than 20 years")
#t1 <- addmargins(t1)
t13 <- as.data.frame.matrix(t13)
t14 <- t13 %>%  mutate(sumcol2_3= t13[,2]+t13[,3])
rownames(t14)[1] <- "ACVS diplomate (large animal/equine)"
rownames(t14)[2] <- "ACVSMR diplomate (equine)	"
rownames(t14)[3] <- "Both ACVS and ACVSMR diplomate	"
#rownames(t12)[4] <- "Both ACVS and ACVSMR diplomate"
#t12 <- t12[x,]


kable(t14, caption = "Contingency table Specialty*FUBM-MSC") 
```

Contingency table	Specialty*FU-PRP
```{r , echo=T}
library(dplyr)
library(knitr)
#Create cross table
t15 <- table(survey_data$Specialty,survey_data$"FU-PRP")

#Selecting order for rows and cols
#y <- c("Greater than once/month", "Greater than 5 times/month", "1-5 times/year", "5-10 times/year", "Never")
#x <- c("Less than 5 years", "5-10 years", "10-20 years", "Greater than 20 years")
#t1 <- addmargins(t1)
t15 <- as.data.frame.matrix(t15)
t16 <- t15 %>%  mutate(sumcol2_3= t15[,2]+t15[,3])
rownames(t16)[1] <- "ACVS diplomate (large animal/equine)"
rownames(t16)[2] <- "ACVSMR diplomate (equine)	"
rownames(t16)[3] <- "Both ACVS and ACVSMR diplomate	"
#rownames(t12)[4] <- "Both ACVS and ACVSMR diplomate"
#t12 <- t12[x,]


kable(t16, caption = "Contingency table Specialty*FU-PRP") 
```


Contingency table	Specialty*FU-IRAP
```{r , echo=T}
library(dplyr)
library(knitr)
#Create cross table
t17 <- table(survey_data$Specialty,survey_data$"FU-IRAP")

#Selecting order for rows and cols
#y <- c("Greater than once/month", "Greater than 5 times/month", "1-5 times/year", "5-10 times/year", "Never")
#x <- c("Less than 5 years", "5-10 years", "10-20 years", "Greater than 20 years")
#t1 <- addmargins(t1)
t17 <- as.data.frame.matrix(t17)
t18 <- t17 %>%  mutate(sumcol2_3= t17[,2]+t17[,3])
rownames(t18)[1] <- "ACVS diplomate (large animal/equine)"
rownames(t18)[2] <- "ACVSMR diplomate (equine)	"
rownames(t18)[3] <- "Both ACVS and ACVSMR diplomate	"
#rownames(t12)[4] <- "Both ACVS and ACVSMR diplomate"
#t12 <- t12[x,]


kable(t18, caption = "Contingency table Specialty*FU-IRAP") 
```

Contingency table	Specialty*FU-PS
```{r , echo=T}
library(dplyr)
library(knitr)
#Create cross table
t19 <- table(survey_data$Specialty,survey_data$"FU-PS")

#Selecting order for rows and cols
#y <- c("Greater than once/month", "Greater than 5 times/month", "1-5 times/year", "5-10 times/year", "Never")
#x <- c("Less than 5 years", "5-10 years", "10-20 years", "Greater than 20 years")
#t1 <- addmargins(t1)
t19 <- as.data.frame.matrix(t19)
t20 <- t19 %>%  mutate(sumcol2_3= t19[,2]+t19[,3])
rownames(t20)[1] <- "ACVS diplomate (large animal/equine)"
rownames(t20)[2] <- "ACVSMR diplomate (equine)	"
rownames(t20)[3] <- "Both ACVS and ACVSMR diplomate	"
#rownames(t12)[4] <- "Both ACVS and ACVSMR diplomate"
#t12 <- t12[x,]


kable(t20, caption = "Contingency table Specialty*FU-PS") 

```

Frequency of use of all biologics 

Frequency of FUA.MSC
```{r , echo=T}
library(ggplot2)
library(dplyr)
library(rlang)
library(knitr)

FUA.MSC <- survey_data1 %>% group_by(FUA.MSC)%>%summarise(Frecuency=length(FUA.MSC), Percentaje = (Frecuency/152)*100)

kable(FUA.MSC, caption = "Frequency of FUA.MSC")  

FUA.MSC %>% ggplot(aes(x=reorder(`FUA.MSC`,Frecuency),y=Frecuency, fill=`FUA.MSC`))+geom_bar(stat="identity")+ xlab("FUA.MSC")+ylab("Total Number")+theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
Frequency of FUBM.MSC


```{r , echo=T}
library(ggplot2)
library(dplyr)
library(rlang)
library(knitr)

FUBM.MSC <- survey_data1 %>% group_by(FUBM.MSC)%>%summarise(Frecuency=length(FUBM.MSC), Percentaje = (Frecuency/152)*100)

kable(FUBM.MSC, caption = "Frequency of FUBM.MSC")  

FUBM.MSC %>% ggplot(aes(x=reorder(`FUBM.MSC`,Frecuency),y=Frecuency, fill= `FUBM.MSC`))+geom_bar(stat="identity")+ xlab("FUBM.MSC")+ylab("Total Number")+theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Frequency FSC.IA

```{r , echo=T}
library(ggplot2)
library(dplyr)
library(rlang)
library(knitr)

FSC.IA <- survey_data1 %>% group_by(FSC.IA)%>%summarise(Frecuency=length(FSC.IA), Percentaje = (Frecuency/152)*100)

kable(FSC.IA, caption = "Frequency FSC.IA")  

FSC.IA %>% ggplot(aes(x=reorder(`FSC.IA`,Frecuency),y=Frecuency, fill= `FSC.IA`))+geom_bar(stat="identity")+ xlab("FSC.IA")+ylab("Total Number")+theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Frequency FSC.IA by Years

```{r , echo=T}
library(ggplot2)
library(dplyr)
library(rlang)
library(knitr)

FSC.IA <- survey_data1 %>% group_by(Years,FSC.IA)%>%summarise(Frecuency=length(FSC.IA), Percentaje = (Frecuency/152)*100)



FSC.IA %>% ggplot(aes(x=reorder(`FSC.IA`,Frecuency),y=Frecuency, fill= `FSC.IA`))+geom_bar(stat="identity")+ xlab("FSC.IA")+ylab("Total Number")+theme(axis.text.x = element_text(angle = 90, hjust = 1))+facet_wrap( ~ Years, ncol=2)
```

